데이터 과학을 위한 저작도구: Computational Documents

### 2020-07-10 cd-code-chunk.Rmd
compile...on mac

---
layout: page
title: "데이터 과학을 위한 저작도구: Computational Documents"
subtitle: "R마크다운 코드 덩어리(Code Chunk)"
author:
  name: "[Tidyverse Korea](https://www.facebook.com/groups/tidyverse/)"
  url: https://www.facebook.com/groups/tidyverse/
  affiliation: Tidyverse Korea
  affiliation_url: https://www.facebook.com/groups/tidyverse/
date: "`r Sys.Date()`"
output:
  html_document: 
    include:
      after_body: footer.html
      before_body: header.html
    theme: journal
    toc: yes
    toc_depth: 2
    toc_float: true
    highlight: tango
    code_folding: show
    number_section: true
    self_contained: no
bibliography: bibliography.bib
csl: biomed-central.csl
editor_options: 
  chunk_output_type: console
---

>>>>

---
layout: page
title: "데이터 과학을 위한 저작도구: Computational Documents"
subtitle: "R마크다운 코드 덩어리(Code Chunk)"
author:
  name: "[Tidyverse Korea](https://www.facebook.com/groups/tidyverse/)"
  url: https://www.facebook.com/groups/tidyverse/
  affiliation: Tidyverse Korea
  affiliation_url: https://www.facebook.com/groups/tidyverse/
date: "`r Sys.Date()`"
output:
  html_document: 
    include:
      after_body: footer.html
      before_body: header.html
    theme: journal
    toc: yes
    toc_depth: 2
    toc_float: true
    highlight: tango
    code_folding: show
    number_section: true
    self_contained: yes
bibliography: bibliography.bib
csl: biomed-central.csl
editor_options: 
  chunk_output_type: console
---
